% !TeX root = paper.tex


\renewcommand{\bibname}{参考文献}
%\addcontentsline{toc}{chapter}{\protect\numberline{参考文献}}
%\addcontentsline{toc}{chapter}{参考文献}
\begin{thebibliography}{99}
\bibitem{1}V.D. Vaughen and T.S. Wilkinson, ''System considerations for
	multispectral image compression designs,'' IEEE Signal
	Process. Mag., vol.12, no.1, pp. 19-31, Jan. 1995.
\bibitem{2}A. Said and W. Pearlman, ''An image multiresolution representation
	for lossless and lossy compression,'' IEEE Trans. Image
	Process., vol.5, no.9, pp.1303-1310, Sept. 1996.
\bibitem{3}小野文孝, ''静止画符号化の新国際標準方式（JPEG2000）の概要,''映
	像情報メディア学会誌, vol.54, no.2, pp.164-171, Feb. 2000.
\bibitem{4}D. Tretter and C.A. Bouman, ''Optimum transform for multispectral
	and multilayer image coding,'' IEEE Trans. Image Process., vol.4, no.3, pp.296-308,
	March 1995.
\bibitem{5}F. Amato, C. Galdi and G. Poggi, ''Embeded zerotree wavelet
	coding on multispectral images,'' IEEE Proc. ICIP 97, vol.1, pp.612-615, 1997.
\bibitem{6}B.R. Epstein, R. Hingorani, J.M. Shapiro and
	M. Czigler, ''Multispectral KLT-wavelet data compression for
	Landsat thematic mapper images,'' Proc. Data Compression
	Conf., IEEE Computer Society Press, pp.200-205, 1992.
\bibitem{7}J.M. Shapiro, S.A. Martucci, and M. Czigler, ''Comparison of
	multispectral Landsat imagery using the embeded zerotree
	wavelet(EZW) algorithm,'' DLPO at Image Compress. Appli. \&
	Innovation Workshop, pp.105-113, March 1994. 
\bibitem{8}J.A. Saghri, A.G. Tescher, and J.T. Reagan, ``Practical transform
	coding of multspectral imagery,'' IEEE Signal Process. Mag.,
	vol.12, no.1, pp.32-43, Jan. 1995.
\bibitem{9}J. Lee, ``Optimized quadtree for Karhunen-Loeve transform in
	multispectral image coding,'' IEEE Trans. Image Process., vol.8, no.4,
	pp.453-461, April 1999.
\bibitem{10}B. Brower, B. Gandhi, D. Couwenhouven and C. Smith, ``ADPCM
	for advanced LANDSAT downlink applications,'' in Proc. 27th
	Asilomar Conf. Signals, Systems and Computers, Nov. 1993. 
\bibitem{11}N.D. Memom, K. Sayood and S.S. Magliveras. ,''Lossless compression
	of multispectral image data,'' IEEE Trans. Geosci. and
	Remote Sensing., vol.32, no.2 , pp.282-289, March 1994.
\bibitem{12}S. Gupta and A. Gersho, ``Feature predictive vector quantization
	of multispectral images,'' IEEE Trans. Geosci. and
	Remote Sensing., vol.30, no.3, pp.491-501, May 1992.
\bibitem{13}K. Irie and R. Kishimoto, ``A study on perfect reconstructive
	subband coding,'' IEEE Trans. Circuits Syst. Video Technol.,
	vol.1, no.1 , pp.42-48, March 1991.
\bibitem{14} 小松 邦紀, 瀬崎 薫, 安田 靖彦, ``濃淡画像の可逆的なサブ
	バンド符号化法'', 信学論（D-II）, vol.J78-D-II, no.3,
	pp.429-436, March 1995.
\bibitem{15}A.R. Calderbank, I. Daubechies, W. Sweldens and B. Yeo, ''Lossless
	image compression using integer to integer wavelet transforms,'' 
	IEEE Proc. ICIP 97, vol.1, pp.596-599, 1997.

\bibitem{16}F.A.M.L. Bruekers and A.W.M.V.D. Enden, ``New networks for
	perfect inversion and perfect reconstruction,'' IEEE
	J. Sel. Areas Commun., vol.10, no.1, pp.130-137,
	Jan. 1992. 
%ブリューカとエンデン「ラダー回路による可逆変換」

\bibitem{17}小松 邦紀, 瀬崎 薫, ``可逆的離散コサイン変換とその画像情報圧
	縮への応用,'' 信学技報, vol.IE97-83, pp.1-6, Nov. 1997.
\bibitem{18}K. Komatsu and K. Sezaki, ''Design for lossless block
	transforms and filter banks for image coding,'' IEICE
	Trans. Fundamentals, vol.E82-A, no.8, pp.1656-1664,
	Aug. 2000.
\bibitem{19}福間 慎治, 岩橋 雅宏, 神林 紀嘉, ``可逆的色変換を用いた色彩
	画像の可逆符号化,'' 信学論（D-II）, vol.J81-D-II, no.11, pp.2680-2684, Nov. 1998.
\bibitem{20} T. Nakachi, T. Fujii, and J. Suzuki,''A unified coding
	algorithm of lossless and near-lossless color image
	compression,'' IEICE Trans. Fundamentals, vol.E83-A, no.2,
	pp. 301-310, Feb. 2000.
\bibitem{21}仲地 孝之, 藤井 竜也, ``可逆KL変換を用いた病理顕微鏡画像符号
	化法の研究,'' 2000信学総大, D16-13, March 2000.
\bibitem{22}鷹合 大輔, 武部 幹, ``可逆WT・KLTを用いるマルチスペクトル画
	像の情報圧縮,'' 信学論（A）, vol.J84-A, no.3, pp.1-11, March
	2001.
\bibitem{23}尾上 守夫, ``画像処理ハンドブック,'' 昭晃堂, pp.554-561, 1987.
\bibitem{24}鷹合 大輔, 武部 幹, ``マルチスペクトル画像のバンド間・バンド
	内相関除去による可逆情報圧縮,'' 第15回DSPシンポジウム講演論文集, pp.475-48, Nov.
	2000.
\bibitem{25}鷹合 大輔, 武部 幹, ``ウェーブレット変換を用いたマルチスペク
	トル画像の情報圧縮符号化法の研究,'' 平成10年度金沢工大卒業論文,
	1998.
\bibitem{26}酒井 幸市，``デジタル画像処理入門,'' コロナ社,1997.
\bibitem{27}榊原 進，``ウェーブレットビギナーズガイド,'' 電機大出版局,
	 1995.
\bibitem{28}武部 幹，``情報圧縮、通信と回路理論,'' 信学技報，IT97-40，July
	1997.
\bibitem{29}Gilbert Strang and Troung Nguyen，``
Wavelet and filter banks,' 'Wellesly Cambridge Press，1996.
\bibitem{30}貴家 仁志，``よくわかるディジタル画像処理,'' CQ出版社，1996.
\bibitem{bk1} "金沢の暮らし", \url{http://www.kanazawa-it.ac.jp}
\bibitem{bk2} 山田 太郎, "金沢の一人暮らし", トンチンカン出版, 2016.
 \end{thebibliography}
 
